Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-22 longoutput.tex
Change colon typeset
Do more work on the amplification

\begin{definition}
	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n\colon U_i\in\set{I,X,Z}}$.
\end{definition}

@@

\begin{lemma}
	$$K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}\colon \ket{y}\in\mathcal{B}^{\otimes n}}$$
\end{lemma}

@@

We now consider the space outside the desired state.
$$S=(\spn\set{\ket{\psi_{circuit}}})^\bot$$
$$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
To combine the Hamiltonians, we apply the projection lemma twice.
$$\exists J_{clock}
=\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
=O(n)=O(T)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
$$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
=\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
\begin{align*}
	S\cap K_{clock}\cap K_{prop}&=S\cap\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}|\ket{y}\in\mathcal{B}^{\otimes n}}\\
	&=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}\colon\braket{x|y}=0}
\end{align*}
$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
\end{proof}

@@

\begin{theorem}
	Let $$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$$ with  $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
	Then there exists an algorithm that accepts $\ket\phi$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$. This algorithm performs only $X$ and $Z$ measurements on $\ket\phi$, and is classical otherwise.
\end{theorem}
\begin{proof}

@@

\begin{theorem}
Let $H$ be a local Hamiltonian with the following properties:
\begin{itemize}
	\item Ground state...?
	\item $\frac{3}{4}$?
\end{itemize}
Then, (some theorem statement)
\end{theorem}
\begin{proof}
	Let $\phi_i$ be the eigenbasis of $H$. Then we can decomposite what the prover sends the verifier as $$\sum_I \alpha_I \ket{\phi_{i_1}}\otimes\ket{\phi_{i_2}}\otimes\ldots\otimes\ket{\phi_{i_{TODO}}}$$.
\end{proof}

>>>>

\begin{definition}
	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}}$.
\end{definition}

@@

\begin{lemma}
	$$K_{clock}\cap K_{prop}=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}: \ket{y}\in\mathcal{B}^{\otimes n}}$$
\end{lemma}

@@

We now consider the space outside the desired state.
$$S=(\spn\set{\ket{\psi_{circuit}}})^\bot$$
$$H_{clock}\big|_S,H_{in}\big|_S,H_{prop}\big|_S$$
To combine the Hamiltonians, we apply the projection lemma twice.
$$\exists J_{clock}
=\frac{\poly\left(\norm{H_{in}\big|_S}\right)}{\lambda\left(H_{clock}\big|_{S\cap K^\bot_{clock}}\right)}
=O(n)=O(T)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}})-\frac{1}{8}$$
$$\exists J_{prop}=\frac{\poly\left(\norm{H_{in}\big|_S+J_{clock}H_{clock}\big|_S}\right)}{\lambda\left(H_{prop}\big|_{S\cap K^\bot_{prop}}\right)}
=\frac{O(n+T)}{\Omega(T^{-2})}=O(T^3)$$
$$\lambda(H_{in}\big|_S+J_{clock}H_{clock}\big|_S+J_{prop}H_{prop}\big|_S)\geq
\lambda(H_{in}\big|_{S\cap K_{clock}\cap K_{prop}})-\frac{1}{4}$$
\begin{align*}
	S\cap K_{clock}\cap K_{prop}&=S\cap\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}|\ket{y}\in\mathcal{B}^{\otimes n}}\\
	&=\set{\sum_{t=0}^TU_t\ldots U_1\ket{y}\otimes\ket{\hat{t}}:\braket{x|y}=0}
\end{align*}
$$\Rightarrow\lambda((H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop})\big|_S)\geq\frac{3}{4}$$
So we set $H_{circuit}=H_{in}+J_{clock}H_{clock}+J_{prop}H_{prop}$, which satisfies the required properties by construction.
\end{proof}

@@

\begin{theorem}\label{ThmXZCheck}
	Let $$H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$$ with  $O(\poly(T))$ nonzero components whose coefficients are each at most $O(\poly(T))$.
	Then there exists an algorithm that accepts $\ket\phi$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$. This algorithm performs only $X$ and $Z$ measurements on $\ket\phi$, and is classical otherwise.
\end{theorem}
\begin{proof}

@@

\begin{theorem}
Let $H$ be a local Hamiltonian with the following properties: TODO $\mathcal{G}_{XZ}$???
\begin{itemize}
	\item has $t$ terms
	\item acts on $q$ qubits
	\item Ground state $0$...?
	\item Something something $\frac{3}{4}$?
\end{itemize}
Then, the prover would send the client $n=O(\poly(t))$ copies... TODO
\end{theorem}
\begin{proof}
Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$. Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(t)}$ for $i\ne1$. We now decomposite what the prover sends in this basis.
$$\sum_I \alpha_I \ket{\phi_{i_1}}\otimes\ket{\phi_{i_2}}\otimes\ldots\otimes\ket{\phi_{i_q}}$$
We categorize the indices $I$ into three types, based on how many $1$s it contains. First kind contains all $1$s. Second contains so little $1$s that... something something Chernoff bound... And the third kind contains the rest.
